### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@c337f170e85889437af63e80d0271b96ee61ca48 🚀

\[
\begin{pmatrix}
    \rho^2 & \rho (1-\rho) \\
    (1-\rho) \rho & (1-\rho)^2
\end{pmatrix} \odot \begin{pmatrix}
    s & (1-s) \\
    (1-s) & s
\end{pmatrix}
\]

@@

The second element we can adjust in this hypothetical classifier is its
bias, specifically its tendency to over-predict interactions. Like
above, we can do so by defining a bias matrix \# Numerical experiments

>>>>

\[
\begin{pmatrix}
    \rho^2 & \rho (1-\rho) \\
    (1-\rho) \rho & (1-\rho)^2
\end{pmatrix} \odot \begin{pmatrix}
    s & (1-s) \\
    (1-s) & s
\end{pmatrix} \,.
\]

@@

The second element we can adjust in this hypothetical classifier is its
bias, specifically its tendency to over-predict interactions. Like
above, we can do so by defining a bias matrix \(\mathbf{B}\), where
interactions are over-predicted with probability \(b\), and express the
final classifier confusion matrix as
\(\mathbf{M}\odot \mathbf{S}\odot \mathbf{B}\), \emph{i.e.}

\[
\begin{pmatrix}
    \rho^2 & \rho (1-\rho) \\
    (1-\rho) \rho & (1-\rho)^2
\end{pmatrix} \odot \begin{pmatrix}
    s & (1-s) \\
    (1-s) & s
\end{pmatrix} \odot \begin{pmatrix}
    b & b \\
    (1-b) & (1-b)
\end{pmatrix}\,.
\]

The final expression for the confusion matrix in which we can regulate
the skill and the bias is

\[
\mathbf{C} = \begin{pmatrix}
    s\times b\times \rho^2 & (1-s)\times b\times \rho (1-\rho) \\
    (1-s)\times (1-b)\times (1-\rho) \rho & s\times (1-b)\times (1-\rho)^2
\end{pmatrix} \,.
\]

\hypertarget{numerical-experiments}{%
\section{Numerical experiments}\label{numerical-experiments}}
